Interactions with Domain Experts

### 2021-01-16 StateOfPractice/Methodology/Interactions with Domain Experts.tex
updated interactions with domain experts

\title{Meeting Agenda with Domain Experts} 
\author{Ao Dong}
\date{\today}

@@

\section{Introduction}
Presenter: \ad{TBD}

A brief introduction to the project. \ad{To be written}

\subsection{3 Steps for Domain Experts}
The domain experts are expected to participate in the following 3 steps:
\begin{itemize}
\item Step 1 - introductory meeting. This is our current meeting, which will
lasts for about one hour.
\item Step 2 - measuring. Usability experiments, modifiability experiments, and
developer interviews are included in this step. More details will be discussed
later in Section \ref{qualities_Measurements}.
\item Step 3 - concluding meeting. Our second and the last meeting, aiming to be
one hour in duration. Results of ranking will be discussed.
\end{itemize}

\subsection{About this Meeting (Introductory Meeting)}
Presenter: \ad{TBD}

The meeting will be roughly one hour. We will follow this document and go
through all the steps.

@@

\subsection{Project Objectives}
\label{project_objectives}
Presenter: Dr.\ Spencer Smith and Dr.\ Jacques Carette \ad{TBD}

The overall objectives are documented in the section Overall Objective of
\href{https://github.com/smiths/AIMSS/blob/master/OverallResearchProposal/ObjectivesAndResearchQuestions.pdf}{Objectives
And Research Questions}.

@@

The research questions are documented in the section Current State of the
Practice Research Questions of
\href{https://github.com/smiths/AIMSS/blob/master/OverallResearchProposal/ObjectivesAndResearchQuestions.pdf}{Objectives
And Research Questions}.

@@

\section{Qualities \& Measurements}
\label{qualities_Measurements}

\subsection{Measurement Template}
\label{measurement_template}
Presenter: \ad{TBD}

\subsection{Survey for Short List Projects}
\label{survey_short_list_projects}
Presenter: \ad{TBD}

Considering the fact that some development teams may ignore our requests for
this interview, We would like to send invitations to all of the teams developing
the software packages in the list. We estimate that there will be a smaller
proportion of them accepting our request. What do you think of
this process?

We also would like to ask the domain experts a modified version of the above
questions. The purpose will be to learn how our domain experts and their
students create software. If we time it right, the interview with the domain
experts is also a chance to do a dry run with our questions.

\subsection{Usability Tests}
\label{usability_tests}
Presenter: Olu \ad{TBD}

Do you have any suggestions? Feedback can be provided later in Task
\ref{task_usability_tests}

\subsection{Modifiability Experiment}
\label{modifiability_experiment}
Presenter:

A brief introduction.

The usability test can be found..

\section{Software List}
Presenter: Ao or Peter \ad{TBD}

In this section, we would like to discuss the list of software packages and the
process of creating and shortening it.

\subsection{Vetting the List of Candidate Software}
\label{vetting_list}
What will be the top 10 software of your choice? Feedback can be provided later
in Task \ref{task_top_10_list}.

@@

\subsection{Domain Analysis}
\label{domain_analysis}
The domain analysis can be found in Section 3.2 of
\href{https://github.com/Ao99/MISEG/blob/master/docs/SRS/SRS.pdf}{SRS for
Medical Imaging Software} or
\href{https://github.com/peter-michalski/LatticeBoltzmannSolvers/blob/master/docs/SRS/CA.pdf}{CA
of Lattice Boltzmann Solvers}.

What do you think of our analysis?  \wss{This is too big a question for the
  domain experts to answer in a reasonable amount of time.  Moreover, without
  more guidance their feedback is likely to be shallow.  I think we are better
  off with a task based inspection, using issues assigned via a GitHub project
  page.  We also will likely be more successful asking for reviews from grad
  students, rather than from faculty members.  We should also consider
  summarizing the commonalities, variabilities and parameters of variation in
  tables, or possibly graphs.}

\subsection{First AHP Ranking}
\label{first_AHP}
Presenter:

A brief introduction.

Do you have any feedback?

\subsection{Final AHP Ranking}
\label{final_AHP}
Presenter:

A brief introduction.

Do you have any feedback?

\section{Publication}
Presenter: Dr.\ Spencer Smith and Dr.\ Jacques Carette \ad{TBD}

@@

\section{Schedule \& Team}
Presenter: \ad{TBD}

@@

@@

\subsection{Review the Usability Tests}
\label{task_usability_tests}
GitHub Issue:
\href{https://github.com/smiths/AIMSS/issues}{https://github.com/smiths/AIMSS/issues}
\ad{To be created}

@@

\noindent Refer to Section \ref{vetting_list}

\subsection{Review the Software List}
\label{task_software_list}
GitHub Issue:
\href{https://github.com/smiths/AIMSS/issues}{https://github.com/smiths/AIMSS/issues}
\ad{To be created}

\noindent Refer to Section \ref{vetting_list}

\subsection{Review the Domain Analysis}
GitHub Issue:
\href{https://github.com/smiths/AIMSS/issues}{https://github.com/smiths/AIMSS/issues}
\pmi{To be created}

\subsection{Review the AHP Ranking and Short List of Software Packages}
GitHub Issue:
\href{https://github.com/smiths/AIMSS/issues}{https://github.com/smiths/AIMSS/issues}
\pmi{To be created}

@@

\subsection{Comment on Final Short List Ranking}
\label{task_final_ranking}
GitHub Issue:
\href{https://github.com/smiths/AIMSS/issues}{https://github.com/smiths/AIMSS/issues}
\pmi{To be created}

>>>>

\title{Interactions with Domain Experts} 
\author{Ao Dong}
\date{\today}

@@

The purpose of the document is to describe the interactions with the domain
experts, which will be through 3 steps as follows,
\begin{itemize}
\item Step 1 - Introductory Meeting in Section \ref{introductory_meeting}. In
this meeting, we will be focusing on introducing the background and objectives
of the project and vetting some details and plans.
\item Step 2 - Measuring in Section \ref{qualities_measurements}. Vetting the
Domain Analysis, usability experiments, modifiability experiments, and
developer interviews are included in this step.
\item Step 3 - Concluding Meeting in Section \ref{concluding_meeting}. Our
second and the last meeting, aiming to be
one hour in duration. Results of ranking will be discussed.
\end{itemize}

\section{Introductory Meeting}
\label{introductory_meeting}

\subsection{Prerequisites}
This section contains the tasks of preparing for the introductory meeting. These
tasks need to be finished before the meeting.

\subsubsection{Top 10 Software List}
\label{top_10_list}

The domain experts need to prepare the top 10 software packages of their choice.
Feedback can be provided in Task \ref{task_top_10_list}.

\subsection{About this Meeting}
Presenter: \ad{TBD}

The meeting will be roughly one hour. We will go
through all the steps in Section \ref{introductory_meeting}.

@@

\subsection{Overall Objective}
\label{overall_objective}
Presenter: Dr.\ Spencer Smith and Dr.\ Jacques Carette \ad{TBD}

As described in the document 
\href{https://github.com/smiths/AIMSS/blob/master/OverallResearchProposal/ObjectivesAndResearchQuestions.pdf}{Objectives
And Research Questions}, the overall objective asks ``What is needed to produce
\{software + artifacts\} sustainably?'' The definitions of \emph{software},
\emph{artifacts} and \emph{sustainably} can be found in the same document. The
term \emph{softifacts} will be used to refer the combination of software and
artifacts.

According to the above document, to answer the above question, we will need to
find answers for these two questions,
\begin{enumerate}
\item ``What softifacts, in addition to the code, are needed?''
\item ``What software engineering principles, processes and methodologies should
be employed?''
\end{enumerate}

@@

The research questions are documented in the section Current State of the
Practice Research Questions of
\href{https://github.com/smiths/AIMSS/blob/master/OverallResearchProposal/ObjectivesAndResearchQuestions.pdf}{Objectives
And Research Questions}. Guided by overall objective in Section
\ref{overall_objective}, these questions focus on researching on ``i) knowledge,
ii) principles, processes
and methodologies, iii) software qualities and iv) the necessary investment of
time and energy''.

@@

\subsection{Vetting the List of Candidate Software}
\label{software_list}

@@

\subsection{Publication}
Presenter: Dr.\ Spencer Smith and Dr.\ Jacques Carette \ad{TBD}

@@

\subsection{Schedule \& Team}
Presenter: \ad{TBD}

@@

\subsection{Introducing the Next Steps}

\section{Qualities \& Measurements}
\label{qualities_measurements}

\subsection{Vetting the Domain Analysis}
\label{domain_analysis}
Task leader: Ao and Peter

The domain analysis can be found in Section 3.2 of
\href{https://github.com/Ao99/MISEG/blob/master/docs/SRS/SRS.pdf}{SRS for
Medical Imaging Software} or
\href{https://github.com/peter-michalski/LatticeBoltzmannSolvers/blob/master/docs/SRS/CA.pdf}{CA
of Lattice Boltzmann Solvers}.

Please review the Figure 1 in \href{https://github.com/Ao99/MISEG/blob/master/docs/SRS/SRS.pdf}{SRS for
Medical Imaging Software} or Figure/Table ? \ad{TBD. It can be a summary of the
commonalities, variabilities and parameters of variation in tables, or possibly
graphs.} in
\href{https://github.com/peter-michalski/LatticeBoltzmannSolvers/blob/master/docs/SRS/CA.pdf}{CA
of Lattice Boltzmann Solvers}.
What do you think of our analysis for the scope of the family, commonalities, and variabilities  for this domain?

Our preference is to have feedback from several graduate students. Feedback can be provided in Task \ref{task_domain_analysis}.

\subsection{Measurement Template}
\label{measurement_template}
Task leader: Ao or Peter

As described in Task \ref{task_measurement_template}, domain experts are
expected to take a look at this template. Feedback are welcome but not required.

\subsection{Survey for Short List Projects}
\label{survey_short_list_projects}
Task leader: Ao or Peter

Considering the fact that some development teams may ignore our requests for
this interview, We would like to send invitations to all of the teams developing
the software packages in the list. We estimate that there will be a smaller
proportion of them accepting our request. What do you think of
this process? Feedback can be provided in Task \ref{task_review_short_list}.

We also would like to ask the domain experts a modified version of the above
questions. The purpose will be to learn how our domain experts and their
students create software. If we time it right, the interview with the domain
experts is also a chance to do a dry run with our questions. We can use Task
\ref{task_short_list_survey} to manage the progress of the survey with domain
experts.

\subsection{Usability Tests}
\label{usability_tests}
Task leader: Olu

Feedback can be provided later in Task
\ref{task_usability_tests}. We can also use the same task to manage the progress of the tests.

\subsection{Modifiability Experiment}
\label{modifiability_experiment}
Task leader: \ad{TBD}

The modifiability experiment can be found at.. \ad{TBD}

Feedback can be provided later in Task
\ref{task_modifiability_experiment}. We can also use the same task to manage the
progress of the tests.

\section{Concluding Meeting}
\label{concluding_meeting}

\subsection{First AHP Ranking}
\label{first_AHP}
Presenter: \ad{TBD}

A brief introduction about the ranking results.

Do you have any feedback? Feedback can be provided in Task \ref{task_first_ranking}.

\subsection{Final AHP Ranking}
\label{final_AHP}
Presenter: \ad{TBD}

A brief introduction about the ranking results for the short list software packages.

Do you have any feedback? Feedback can be provided in Task \ref{task_final_ranking}.

@@

\noindent Refer to Section \ref{top_10_list}

\subsection{Vet the Software List}
\label{task_software_list}
GitHub Issue:
\href{https://github.com/smiths/AIMSS/issues}{https://github.com/smiths/AIMSS/issues}
\ad{To be created}

\noindent Refer to Section \ref{software_list}

\subsection{Vet the Domain Analysis}
\label{task_domain_analysis}
GitHub Issue:
\href{https://github.com/smiths/AIMSS/issues}{https://github.com/smiths/AIMSS/issues}
\pmi{To be created}

\subsection{Read the Measurement Template}
\label{task_measurement_template}
GitHub Issue:
\href{https://github.com/smiths/AIMSS/issues}{https://github.com/smiths/AIMSS/issues}
\ad{To be created}

\noindent Refer to Section \ref{measurement_template}

\subsection{Review the Process of Creating a Short List}
\label{task_review_short_list}
GitHub Issue:
\href{https://github.com/smiths/AIMSS/issues}{https://github.com/smiths/AIMSS/issues}
\ad{To be created}

\noindent Refer to Section \ref{survey_short_list_projects}

\subsection{Take the Survey for the Short List Projects}
\label{task_short_list_survey}
GitHub Issue:
\href{https://github.com/smiths/AIMSS/issues}{https://github.com/smiths/AIMSS/issues}
\ad{To be created}

\noindent Refer to Section \ref{survey_short_list_projects}

\subsection{Participate in the Usability Tests}
\label{task_usability_tests}
GitHub Issue:
\href{https://github.com/smiths/AIMSS/issues}{https://github.com/smiths/AIMSS/issues}
\ad{To be created}

@@

\subsection{Participate in the Modifiability Experiment}
\label{task_modifiability_experiment}
GitHub Issue:
\href{https://github.com/smiths/AIMSS/issues}{https://github.com/smiths/AIMSS/issues}
\ad{To be created}

\noindent Refer to Section \ref{modifiability_experiment}

\subsection{Review the First AHP Ranking}
\label{task_first_ranking}
GitHub Issue:
\href{https://github.com/smiths/AIMSS/issues}{https://github.com/smiths/AIMSS/issues}
\pmi{To be created}

@@

\subsection{Review the Final Short List Ranking}
\label{task_final_ranking}
GitHub Issue:
\href{https://github.com/smiths/AIMSS/issues}{https://github.com/smiths/AIMSS/issues}
\pmi{To be created}
